---
title: "Dharma_summary"
author: "Jessica Gephart"
date: "9/22/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Background data and 
library(tidyverse)
library(knitr)
# Load data
data_raw <- read.csv("Data/project_7458_kiribati_named.csv", na.strings='.') 

# When column A “FactID” = the following, please delete the record:
FactID_remove <- c(8928972, 8928976, 8929006, 8930961, 8931112, 8931114, 8931115, 8931118, 8932937, 8933375, 8933391, 8936960,
  8936961, 8936963, 8936965, 8973411, 8977546, 8994095, 9015753, 9015785, 9047885, 9047887, 9051314, 9062095,
  9062097, 9063402, 9119004, 9119030, 9119061, 9119506, 9119508, 8933361, 8933361, 9119065, 8929045, 8929040,
  8929040, 8931117, 8998741, 8931110, 9062101, 9062101, 9062101)

# Functions
clean.named <- function(DATA, FactID_remove){
  DATA$L1_q16_date_of_interview <- as.Date(DATA$L1_q16_date_of_interview, tryFormats = c("%m/%d/%y"))
  DATA$L1_q1_dob <- as.Date(DATA$L1_q1_dob, tryFormats = c("%m/%d/%y"))
  
  # Columns Q – Z will only have one answer per row to locate the community, 
  # could you collapse this so it just has this information in one column?
  # L1_q125_which_community_are_you_in:L1_q135_what_community_are_you_in
  DATA$community <- c()
  community_cols <- c("L1_q125_which_community_are_you_in", 
                      "L1_q126_which_community_are_you_in",
                      "L1_q127_which_community_are_you_in",
                      "L1_q128_which_community_are_you_in",
                      "L1_q129_which_community_are_you_in",
                      "L1_q130_which_community_are_you_in",
                      "L1_q131_which_community_are_you_in",
                      "L1_q132_which_community_are_you_in",
                      "L1_q133_which_community_are_you_in",
                      "L1_q134_which_community_are_you_in",
                      "L1_q135_which_community_are_you_in")
  for(i in 1:length(community_cols)){
    DATA$community[which(!is.na(DATA[[paste(community_cols[i])]]))] <- 
      as.character(DATA[[paste(community_cols[i])]][which(!is.na(DATA[[paste(community_cols[i])]]))])
  }
  
  # Change column data type where needed
  DATA$L1_q227_lastmealtime <- as.character(DATA$L1_q227_lastmealtime)
  
  CLEAN <- DATA %>% 
    # Delete columns CT to JC
    select(-c(L1_q41_ciguatera:L1_q220_duplicate_of_during_the_past_year_on_average_how_many_hours_did_you_spend_per_week_sitting_at_home_watching_tv_listening_to_radio_etc)) %>%
    # Remove L1_q125_which_community_are_you_in:L1_q135_what_community_are_you_in since they were collapsed into "community"
    select(-c(L1_q125_which_community_are_you_in:L1_q135_what_community_are_you_in)) %>%
    # Remove blank records (where gender and DOB are NA)
    filter(is.na(L1_q1_dob) == FALSE & is.na(L1_q3_gender) == FALSE) %>%
    # When column A “FactID” = the following, please delete the record:
    filter(!(fact_0_id %in% FactID_remove)) %>%
    # In column DC “deleted”, when TRUE, please delete/hide from analysis
    filter(deleted == FALSE) %>%
    # Use column K and L to calculate age days
    mutate(age_days = difftime(L1_q16_date_of_interview, L1_q1_dob, units="days")) %>%
    
    # Calculate age groups
    mutate(age_group = case_when(
      (age_days <= (12*365.25)) ~ "under 12",
      (age_days > (12*365.25) & age_days <= (20*365.25)) ~ "12-20",
      (age_days > (20*365.25) & age_days <= (40*365.25)) ~ "20-40",
      (age_days > (40*365.25)) ~ "over 40")) %>%
    
    # Column BY: Create a fever category to indicate no fever <100.4 and fever > or = 100.4
    mutate(fever_YN = case_when(
      L1_q229_temperature < 100.4 ~ "N", 
      L1_q229_temperature >= 100.4 ~ "Y"
    )) %>%
    
    # Columns BZ and CA: Categorize blood pressure
    # Blood pressure:
    # - Normal: Less than 120/80 mm Hg;
    # - Elevated: Systolic between 120-129 and diastolic less than 80;
    # - Stage 1: Systolic between 130-139 or diastolic between 80-89;
    # - Stage 2: Systolic at least 140 or diastolic at least 90 mm Hg;
    # - Hypertensive crisis: Systolic over 180 and/or diastolic over 120
    mutate(BloodPressure_status = case_when(
      (L1_q239_systolic < 120 & L1_q240_diastolic < 80) ~ "Normal",
      (L1_q239_systolic >= 120 & L1_q239_systolic < 129 & L1_q240_diastolic <= 80) ~ "Elevated",
      (L1_q239_systolic >= 130 & L1_q239_systolic < 140 | 
         L1_q240_diastolic >= 80 & L1_q240_diastolic <= 89) ~ "Stage 1",
      (L1_q239_systolic >= 140 & L1_q239_systolic <= 180 |
         L1_q240_diastolic >= 90 & L1_q240_diastolic <= 120) ~ "Stage 2",
      (L1_q239_systolic >= 180 | L1_q240_diastolic >= 120) ~ "Hypertensive Crisis"
    )) %>%
    
    # Column CC for glucose
    # - Between 3.9-7.2 mmol/L is normal regardless of column BW. Categorize as normal
    # - Above 7.2 if BW is before 4am (ie evening before) is too high. Categorize as hyperglycemic.
    # - Less than 10.0mmol/L is normal if column BW is between 4am -7am. Above this and categorize as hyperglycemic.
    # - Below 3.9, categorize as hypoglycemic.
    #mutate(Glucose_status = case_when(
    #  ((L1_q63_glucose > 7.21 & L1_q227_lastmealtime %in% c("5pm", "6pm", "7pm", "8pm", "9pm", 
    #                                                              "10pm", "11pm", "12am", "1am", "2am",
    #                                                              "3am")) | 
    #     (L1_q63_glucose > 10 & L1_q227_lastmealtime %in% c("4am", "5am", "6am", "7am"))) ~ "Hyperglycemic",
    #  (L1_q63_glucose > 3.9 & L1_q63_glucose < 7.2) ~ "Normal",
    #  L1_q63_glucose < 3.9 ~ "Hypoglycemic"
    #  )) %>%
    # Data recorded as mg/dL. Use Hypoglycemia when <70 mg/dL, Normal 70 - 180 mg/dL, Hyperglycemia when >180mg/dL 
    # (don't have to do last meal for the moment)
  mutate(Glucose_status = case_when(
    age_days < (12*365.25) ~ "under 12",
    (age_days >= (12*365.25) & L1_q63_glucose >= 180) ~ "Hyperglycemic",
    (age_days >= (12*365.25) & L1_q63_glucose > 70 & L1_q63_glucose < 180) ~ "Normal",
    (age_days >= (12*365.25) & L1_q63_glucose <= 70) ~ "Hypoglycemic"
    )) %>%
  
    # Calculate anemia status (refer to table)
  mutate(anemia_status = case_when(
    ((age_days < (5*365.25) & L1_q234_measure_hemoglobin_g_dl > 11) |
       (age_days >= (5*365.25) & age_days < (12*365.25) & L1_q234_measure_hemoglobin_g_dl > 11.5) |
       (age_days >= (12*365.25) & age_days < (15*365.25) & L1_q234_measure_hemoglobin_g_dl > 12) |
       (age_days >= (15*365.25) & age_days < (50*365.25) & L1_q3_gender == "F" & L1_q51_breastfeeding_pregnant_lactating.001 != "Pregnant" & L1_q234_measure_hemoglobin_g_dl > 12) |
       (age_days >= (15*365.25) & age_days < (50*365.25) & L1_q3_gender == "F" & L1_q51_breastfeeding_pregnant_lactating.001 == "Pregnant" & L1_q234_measure_hemoglobin_g_dl > 11) |
       (age_days >= (15*365.25) & age_days < (50*365.25) & L1_q3_gender == "M" & L1_q234_measure_hemoglobin_g_dl > 13))~ "non-anemic",
    
    ((age_days < (5*365.25) & L1_q234_measure_hemoglobin_g_dl >= 10 & L1_q234_measure_hemoglobin_g_dl < 11) |
       (age_days >= (5*365.25) & age_days < (12*365.25) & L1_q234_measure_hemoglobin_g_dl >= 11 & L1_q234_measure_hemoglobin_g_dl < 11.5) |
       (age_days >= (12*365.25) & age_days < (15*365.25) & L1_q234_measure_hemoglobin_g_dl >= 11 & L1_q234_measure_hemoglobin_g_dl < 12) |
       (age_days >= (15*365.25) & age_days < (50*365.25) & L1_q3_gender == "F" & L1_q51_breastfeeding_pregnant_lactating.001 != "Pregnant" & L1_q234_measure_hemoglobin_g_dl >= 11 & L1_q234_measure_hemoglobin_g_dl < 12) |
       (age_days >= (15*365.25) & age_days < (50*365.25) & L1_q3_gender == "F" & L1_q51_breastfeeding_pregnant_lactating.001 == "Pregnant" & L1_q234_measure_hemoglobin_g_dl >= 10 & L1_q234_measure_hemoglobin_g_dl < 11) |
       (age_days >= (15*365.25) & age_days < (50*365.25) & L1_q3_gender == "M" & L1_q234_measure_hemoglobin_g_dl >= 11 & L1_q234_measure_hemoglobin_g_dl < 13))~ "mild",
    
        ((age_days < (5*365.25) & L1_q234_measure_hemoglobin_g_dl >= 7 & L1_q234_measure_hemoglobin_g_dl < 10) |
       (age_days >= (5*365.25) & age_days < (12*365.25) & L1_q234_measure_hemoglobin_g_dl >= 8 & L1_q234_measure_hemoglobin_g_dl < 11) |
       (age_days >= (12*365.25) & age_days < (15 *365.25) & L1_q234_measure_hemoglobin_g_dl >= 8 & L1_q234_measure_hemoglobin_g_dl < 11) |
       (age_days >= (15*365.25) & age_days < (50*365.25) & L1_q3_gender == "F" & L1_q51_breastfeeding_pregnant_lactating.001 != "Pregnant" & L1_q234_measure_hemoglobin_g_dl >= 8 & L1_q234_measure_hemoglobin_g_dl < 11) |
       (age_days >= (15*365.25) & age_days < (50*365.25) & L1_q3_gender == "F" & L1_q51_breastfeeding_pregnant_lactating.001 == "Pregnant" & L1_q234_measure_hemoglobin_g_dl >= 7 & L1_q234_measure_hemoglobin_g_dl < 10) |
       (age_days >= (15*365.25) & age_days < (50*365.25) & L1_q3_gender == "M" & L1_q234_measure_hemoglobin_g_dl >= 8 & L1_q234_measure_hemoglobin_g_dl < 11))~ "moderate",
    
        ((age_days < (5*365.25) & L1_q234_measure_hemoglobin_g_dl < 7) |
       (age_days >= (5*365.25) & age_days < (12*365.25) & L1_q234_measure_hemoglobin_g_dl < 8) |
       (age_days >= (12*365.25) & age_days < (15 *365.25) & L1_q234_measure_hemoglobin_g_dl < 8) |
       (age_days >= (15*365.25) & age_days < (50*365.25) & L1_q3_gender == "F" & L1_q51_breastfeeding_pregnant_lactating.001 != "Pregnant" & L1_q234_measure_hemoglobin_g_dl < 8) |
       (age_days >= (15*365.25) & age_days < (50*365.25) & L1_q3_gender == "F" & L1_q51_breastfeeding_pregnant_lactating.001 == "Pregnant" & L1_q234_measure_hemoglobin_g_dl < 7) |
       (age_days >= (15*365.25) & age_days < (50*365.25) & L1_q3_gender == "M" & L1_q234_measure_hemoglobin_g_dl < 8))~ "severe", 
    age_days >= (50*365.25) ~ "over 50"
  )) %>% 
    
    # Columns CG, CH, and CJ cholesterol
    # The following levels are considered to be "good" in healthy people:
    # -	Total cholesterol: Levels below 200 mg/dL (5.2 mmol/L)
    # -	LDL cholesterol: Levels below 130 mg/dL (3.4 mmol/L)
    # -	HDL cholesterol: Levels above 40 mg/dL (1 mmol/L) in men and above 50 mg/dL (1.3 mmol/L) in women
    # If above the TC or LDL, or below in the HDL, then please indicate cholesterol risk.
    mutate(cholesterol_status = case_when(
      age_days < (12*365.25) ~ "under 12",
      (age_days >= (12*365.25) & L1_q60_tc < 200 & L1_q61_hdl > 40 & L1_q64_ldl < 130) ~ "Normal",
      (age_days >= (12*365.25) & L1_q60_tc >= 200 | L1_q61_hdl <= 40 | L1_q64_ldl >= 130) ~ "At risk"
    )) %>% 
    
    # Column CI for triglycerides
    # Categorize triglyceride levels based on the following:
    # (1) low-normal triglycerides (<100 mg/dL); 
    # (2) high-normal triglycerides (100–149 mg/dL); 
    # (3) borderline hypertriglyceridemia triglycerides (150–199 mg/dL); 
    # (4) moderate hypertriglyceridemia triglycerides (200–499 mg/dL); 
    # (5) severe hypertriglyceridemia triglycerides (≥500 mg/dL)
    mutate(triglycerides_status = case_when(
      age_days < (12*365.25) ~ "under 12",
      (age_days >= (12*365.25) & L1_q62_triglycerides < 100) ~ "Low-normal",
      (age_days >= (12*365.25) & L1_q62_triglycerides >= 100 & L1_q62_triglycerides < 150) ~ "High-normal",
      (age_days >= (12*365.25) & L1_q62_triglycerides >= 150 & L1_q62_triglycerides < 200) ~ "Borderline hypertriglyceridemia",
      (age_days >= (12*365.25) & L1_q62_triglycerides >= 200 & L1_q62_triglycerides < 500) ~ "Moderate hypertriglyceridemia",
      (age_days >= (12*365.25) & L1_q62_triglycerides >= 500) ~ "Severe hypertriglyceridemia"
    )) %>%
    
    # Column CN for diabetes
    # For people without diabetes, the normal range for the hemoglobin A1c level is between 4% and 5.6%. 
    # Hemoglobin A1c levels between 5.7% and 6.4% mean you have a higher chance of getting diabetes. 
    # Levels of 6.5% or higher mean you have diabetes. Please categorize as such. 
    mutate(diabetes_status = case_when(
      age_days < (12*365.25) ~ "under 12",
      (age_days >= (12*365.25) & L1_q59_diabetes < 5.7) ~ "Normal",
      (age_days >= (12*365.25) & L1_q59_diabetes >= 5.7 & L1_q59_diabetes < 6.5) ~ "At risk",
      (age_days >= (12*365.25) &L1_q59_diabetes >= 6.5) ~ "Diabetic"
    ))
  
  CLEAN$age_group <- ordered(CLEAN$age_group, levels = c("under 12", "12-20", "20-40", "over 40"))
  
  CLEAN$fever_YN <- as.factor(CLEAN$fever_YN)
  CLEAN$BloodPressure_status <- as.factor(CLEAN$BloodPressure_status)
  CLEAN$BloodPressure_status <- ordered(CLEAN$BloodPressure_status, levels = c(
    "Normal", "Elevated", "Stage 1", "Stage 2", "Hypertensive Crisis"
  ))
  
  CLEAN$Glucose_status <- as.factor(CLEAN$Glucose_status)
  CLEAN$Glucose_status <- ordered(CLEAN$Glucose_status, levels = c(
    "Normal", "Hypoglycemic", "Hyperglycemic", "under 12"
    ))

  CLEAN$anemia_status <- as.factor(CLEAN$anemia_status)
  CLEAN$anemia_status <- ordered(CLEAN$anemia_status, levels = c(
    "non-anemic", "mild", "moderate", "severe", "over 50"
  ))
  
  CLEAN$cholesterol_status <- as.factor(CLEAN$cholesterol_status)
  CLEAN$cholesterol_status <- ordered(CLEAN$cholesterol_status, levels = c(
    "Normal", "At risk", "under 12"
  ))
  
  CLEAN$triglycerides_status <- as.factor(CLEAN$triglycerides_status)
  CLEAN$triglycerides_status <- ordered(CLEAN$triglycerides_status, levels = c(
    "Low-normal", "High-normal", "Borderline hypertriglyceridemia", 
    "Moderate hypertriglyceridemia", "Severe hypertriglyceridemia" , "under 12"
  ))

  
  CLEAN$diabetes_status <- as.factor(CLEAN$diabetes_status)
  CLEAN$diabetes_status <- ordered(CLEAN$diabetes_status, levels = c(
    "Normal", "At risk", "Diabetic", "under 12"
  ))
  
    return(CLEAN)
}

# Clean data
data_clean <- clean.named(data_raw, FactID_remove = FactID_remove)
write.csv(data_clean, "Outputs/Dharma_cleaned.csv", row.names = FALSE)

# Create a unique list of responses from column AA so that I can trace where these are with local consultation
place_of_birth <- unique(data_clean$L1_q236_place_of_birth)
write.csv(data.frame(place_of_birth = place_of_birth), "Outputs/place_of_birth.csv", row.names = FALSE)
```

## Notes on the raw data
Need to correct breastfeeding/lactating resonses (see below).

## The number of completed interviews by sex and age categories
```{r, echo=FALSE, message=FALSE, warning=FALSE}
age_sex <- data_clean %>%
  group_by(age_group, L1_q3_gender) %>%
  tally()
colnames(age_sex) <- c("Age", "Sex", "Count")
kable(age_sex)

```

## Pregnant and lactating women
```{r, echo=FALSE, message=FALSE, warning=FALSE}
n.lactating <- sum(data_clean$L1_q51_breastfeeding_pregnant_lactating.000 == "Lactating", na.rm = TRUE)
n.pregnant <- sum(data_clean$L1_q51_breastfeeding_pregnant_lactating.001 == "Pregnant", na.rm = TRUE)
n.breastfeeding <- sum(data_clean$L1_q51_breastfeeding_pregnant_lactating.003 == "Breastfeeding", na.rm = TRUE)
n.F12to40 <- age_sex %>% 
  filter(Sex == "F" & Age %in% c("12-20", "20-40"))
n.F12to40 <-  sum(n.F12to40$Count)

```
The percent of lactacting women between the ages of 12 and 40 is `r round(100*(n.lactating/n.F12to40))`%. 
The percent of pregnant women between the ages of 12 and 40 is `r round(100*(n.pregnant/n.F12to40))`%. 
The percent of breastfeeding women between the ages of 12 and 40 is `r NA`%.

NOTE: The breastfeeding stat should refer to children who are breastfeeding. The women over 3 reported as breastfeeding should be changed to lactating.


## Food preference ranks (1 = most preferred; 5 = least preferred)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Summarize L1_q206_what_rank_would_you_give_mutton_flaps:L1_q195_what_rank_would_you_give_tuna
food_ranks <- data_clean %>% 
  select(L1_q206_what_rank_would_you_give_mutton_flaps:L1_q195_what_rank_would_you_give_tuna) 
colnames(food_ranks) <- c("Mutton flaps", "Beef", "Pork", "Turkey tails", "Chicken", 
                    "Spam", "Canned corn beef", "Tin fish", "Reef fish (e.g., snapper)", 
                    "Mackerel", "Tuna")

kable(sort(round(colMeans(food_ranks, na.rm = TRUE), digits = 2)), col.names = "Ave. Rank")


```

## Food preferences by age, sex

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tab <- data_clean %>% 
  group_by(L1_q3_gender, age_group) %>%
  select(L1_q3_gender, age_group, L1_q206_what_rank_would_you_give_mutton_flaps:L1_q195_what_rank_would_you_give_tuna) %>%
  summarise_all(funs(round(mean(.,na.rm = TRUE), digits = 2)))

colnames(tab) <- c("Sex", "Age", "Mutton flaps", "Beef", "Pork", "Turkey tails", "Chicken", 
                    "Spam", "Canned corn beef", "Tin fish", "Reef fish (e.g., snapper)", 
                    "Mackerel", "Tuna")

kable(t(tab)) 

```

## Fever summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tab <- data_clean %>% 
  group_by(fever_YN) %>%
  count()

kable(tab)
```

i. For fever, this is normal because we have been missing thermometers for lots of events, and I think some of the readings are in Celsius and so need to be converted as well. 
- The weird ones I see are 35 (which is probably C) and 67 (which doesn't make sense for either F or C). If there is a cutoff point, I could add in a line that says if temp is below that value, then convert to F. 

## Blood Pressure summary

```{r, echo=FALSE, warning=FALSE, message=FALSE}
tab <- data_clean %>% 
  group_by(BloodPressure_status) %>%
  count()

kable(tab)
```

## Glucose summary

```{r, echo=FALSE, warning=FALSE, message=FALSE}
tab <- data_clean %>% 
  filter(Glucose_status != "under 12") %>%
  group_by(Glucose_status) %>%
  count()

kable(tab)
```

## Anemia summary

```{r, echo=FALSE, warning=FALSE, message=FALSE}

tab <- data_clean %>% 
  filter(anemia_status != "over 50") %>%
  group_by(anemia_status) %>%
  count()

kable(tab)
```

## Cholesterol summary

```{r, echo=FALSE, warning=FALSE, message=FALSE}
tab <- data_clean %>% 
  filter(cholesterol_status != "under 12") %>%
  group_by(cholesterol_status) %>%
  count()

kable(tab)
```

## Trigycerides summary

```{r, echo=FALSE, warning=FALSE, message=FALSE}
tab <- data_clean %>% 
  filter(triglycerides_status != "under 12") %>%
  group_by(triglycerides_status) %>%
  count()

kable(tab)
```

## Diabetes summary

```{r, echo=FALSE, warning=FALSE, message=FALSE}
tab <- data_clean %>% 
  filter(diabetes_status != "under 12") %>%
  group_by(diabetes_status) %>%
  count()

kable(tab)
```