---
title: "Exploratory figures for CNHS"
author: "Kelvin Gorospe and Jessica Gephart"
date: "6/10/2020"
output: pdf_document
---


Notes for Mike:

* Is it correct to remove the 0/1 columns in the market Survey data?
* Is there a way to automate this process on your end? So that code still works with new data
* Where is the market availability data that we had in the last iteration?
* [name of product]_roster is the availability data
* What is the meaning of NA in the multiselect variable columns?
* "." and ".a" in STATA both mean missing. Refer to Mike's May 27 email for example (and to check for consistency with R)
* Why does VRS have household info and anemia info?
* Why are these output as different files (vrs, market, etc. each broken into multiple separate files)
* It is easiest to have the fewest number possible
* Are they going to translate the HIES iKiribati responses?
* Variable labels are cut off (how do we get the full answers back?) see: var_labels
* How to standardize units when none is given (e.g., question == Travel time outside boundary in outsideRoster dataset includes "12", "3", "30 minutes", "1 hour", etc)
* Is a response of "zero" the same as blank response? 
* What's the difference between interview__key and interview__id? Currently using both to join eventRoster, fishRoster, etc with vrs data to get island information

Suggested path forward:
 
1. Write out tidy versions of each data set and share csv
2. Write functions to visualize each question type:
     - Multi- and single-select, produce bar chart
     - Integer, produce bar chart
     - Continuous, produce histogram and (TBD: box and whisker)
     - Free response, compile unique answers with unique IDs for translation, question, island, possibly role
3. Loop through data and produce pdf of all plots
4. TBD: Start to create summaries by village/island
 


```{r setup, echo = FALSE, warning = FALSE, message = FALSE}

### NOTE: only use this RMD file to create archipelago-wide plots (not grouped by island)
### NOTE: to create plots grouped by island, use the "per_island" RMD file

knitr::opts_chunk$set(echo = FALSE)
library(haven)
library(tidyverse)
library(magrittr)
library(ggplot2)

#___________________________________________________________________________________________#
# Read in dta files
#___________________________________________________________________________________________#
#datadir <- file.path(getwd(), "Data", "HIES_raw_19May20")
#outdir <- file.path(getwd(), "Outputs")
datadir <- "/Volumes/jgephart/Kiribati/HIES_raw_19May20"
outdir <- "/Volumes/jgephart/Kiribati/Outputs"
source("R_scripts/cleaning_functions.R")
source("R_scripts/plotting_functions.R")

```

## Fisheries data
### *Multi-response questions*


```{r, warning = FALSE}

#___________________________________________________________________________________________#
# Clean fisheries data
#___________________________________________________________________________________________#
fisheries <- read_dta(file.path(datadir, "Fisheries", "Fisheries.dta"))


fisheries <- clean_data(fisheries)[[1]]

# Extract variable label attributes
var_labels <- clean_data(fisheries)[[2]]

# Change class to character to allow left_join without warning below
var_labels <- var_labels %>%
  mutate(col.names = as.character(col.names))

# Make tidy
fisheriesTidy <- tidy_data(df = fisheries, pivot_col_1 = "sex", pivot_col_last = "p922n3", var_labels = var_labels, question_no = TRUE) # question_no = TRUE applies to fisheries data where col.labels includes a third column for question.no

write.csv(fisheriesTidy, file.path(outdir, "fisheriesTidy.csv"), row.names = FALSE)
```


```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize fisheries data
#___________________________________________________________________________________________#
# Bar graphs and Histograms of single/multi-select questions


# Plot bar graph for each multi-select question
plotDF_multiselect <- fisheriesTidy %>%
  filter(!is.na(option)) %>%
  filter(response == "1")

plot_multi_response(plotDF_multiselect)


```


## Fisheries continued...
### *Single response questions*



```{r, fig.height = 8, results = 'asis'}

# List short-answer, fill-in response questions here:
fill_in_questions <- c("p903n", "p921n", "p922n1", "p922n2")

# Plot histogram for each single response question while removing zeroes
plotDF_single <- fisheriesTidy %>%
  filter(is.na(option)) %>%
  filter(question.no %in% fill_in_questions == FALSE) # remove "other" responses

plot_single_response(plotDF_single, bin_n = 20)
  

# Output short answer responses for translation
other_answers <- fisheriesTidy %>% 
  filter(question.no %in% fill_in_questions) %>%
  filter(response != "") %>% 
  unique()

write.csv(other_answers, file.path(outdir, "fisheries_other_answers.csv"), row.names = FALSE)




```



## Other Fisheries (p903r) data


```{r, warning = FALSE}

#___________________________________________________________________________________________#
# Clean fisheries data
#___________________________________________________________________________________________#
fisheries_903 <- read_dta(file.path(datadir, "Fisheries", "p903r.dta"))

fisheries_903 <- clean_data(fisheries_903)[[1]]

# Extract variable label attributes
var_labels <- clean_data(fisheries_903)[[2]]

# Change class to character to allow left_join without warning below
var_labels <- var_labels %>%
  mutate(col.names = as.character(col.names))

# Make tidy
fisheriesTidy_903 <- tidy_data(df = fisheries_903, pivot_col_1 = "p904", pivot_col_last = "p910", var_labels = var_labels, question_no = TRUE) # question_no = TRUE applies to fisheries data where col.labels includes a third column for question.no

write.csv(fisheriesTidy_903, file.path(outdir, "fisheriesTidy_903.csv"), row.names = FALSE)


# Output short answer responses for translation
short_answers <- c("other method of transportation")
# Short answers - units need to be standardized and some responses need to be translated

other_answers <- fisheriesTidy_903 %>% 
  filter(question %in% short_answers) %>%
  filter(response != "") %>% 
  unique() %>%
  arrange(question)

write.csv(other_answers, file.path(outdir, "fisheries_903R_other_answers.csv"), row.names = FALSE)


# Filter out short answer responses before moving on to plotting data subsets
fisheriesTidy_903 <- fisheriesTidy_903 %>%
  filter(question %in% short_answers == FALSE)




event_subsets <- fisheriesTidy_903 %>%
  select(p903r__id) %>%
  unique()

event_subsets


```


## *Fishing Method: Trolling, jigging or deep water line fishing*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Trolling, jigging or deep water line fishing - Te kasiki") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)


```


## *Fishing Method: Handline (drop stone, pole fishing, rod &amp; reel) - Te karekare*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Handline (drop stone, pole fishing, rod &amp; reel) - Te karekare") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Fishing Method: Gleaning / Collecting*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Gleaning / Collecting") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Fishing Method: Other (note)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Other (note)") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Fishing Method: Spearfishing night (Te katebe te tairiki)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Spearfishing night (Te katebe te tairiki)") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Fishing Method: Spearfishing day ((Te katebe te ngaina)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Spearfishing day ((Te katebe te ngaina)") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Fishing Method: Net (beach seine, gill, cast) - Te karaun*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Net (beach seine, gill, cast) - Te karaun") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```
## *Fishing Method: Freediving / diving without SCUBA (Te tebo)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Freediving / diving without SCUBA (Te tebo)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```
## *Fishing Method: Traps (Te uu)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Traps (Te uu)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```
## *Fishing Method: Diving with SCUBA (Te tebo me te bwai n ikeike)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Diving with SCUBA (Te tebo me te bwai n ikeike)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## p903 continued: CPUE

```{r, fig.height = 8, results = 'asis'}

cpue_pivot <- fisheriesTidy_903 %>%
  filter(question %in% c("hours spent on the trip to access current method",
                         "number of fishing trips",
                         "hours spent on current method",
                         "weight of catch using current method")) %>%
  select(-question.no) %>%
  pivot_wider(names_from = question, values_from = response)

cpue_summary <- cpue_pivot %>%
  mutate_at(vars(`hours spent on the trip to access current method`,
                 `weight of catch using current method`, 
                 `number of fishing trips`,
                 `hours spent on current method`), as.numeric) %>%
  group_by(interview__id, hm_basic__id, p903r__id) %>% # group_by interviewee, household member (sometimes multiple interviews per houselhold) and fishing gear
  summarise(cpue = `weight of catch using current method` / (`hours spent on the trip to access current method` * `hours spent on current method` * `number of fishing trips`)) %>%
  ungroup()


### NOTE: There are zeroes in all time columns (i.e., `hours spent on the trip to access current method`, `hours spent on current method`, `number of fishing trips`)
# meaning no matter which column is used, CPUE is undefined (catch divided by zero) for certain respondents

# FIX IT - turn this into a function?
for (i in 1:length(unique(cpue_summary$p903r__id))) {
  
  
  fishing_method <- unique(cpue_summary$p903r__id)[i]
  
  cpue_plot <- cpue_summary %>% 
    filter(p903r__id == fishing_method) %>%
    filter(cpue != "Inf") %>% # filters out when denominator is zero
    filter(is.na(cpue)==FALSE) # filters out when numerator and denominator is zero
  
  p <- ggplot(cpue_plot, aes(x = cpue)) +
    geom_histogram(bins = 20) +
    labs(title = fishing_method, y = "", x = "CPUE")

  # Print out each plot within R
  print(p)
  # Go to new page before printing next figure
  cat("\n\n\\newpage\n")
      
  
}


```

## Other Fisheries (p922r) data


```{r, warning = FALSE}

#___________________________________________________________________________________________#
# Clean fisheries data
#___________________________________________________________________________________________#
fisheries_922 <- read_dta(file.path(datadir, "Fisheries", "p922r.dta"))

fisheries_922 <- clean_data(fisheries_922)[[1]]

# Extract variable label attributes
var_labels <- clean_data(fisheries_922)[[2]]

# Change class to character to allow left_join without warning below
var_labels <- var_labels %>%
  mutate(col.names = as.character(col.names))

# Make tidy
fisheriesTidy_922 <- tidy_data(df = fisheries_922, pivot_col_1 = "p923", pivot_col_last = "p925", var_labels = var_labels, question_no = TRUE) # question_no = TRUE applies to fisheries data where col.labels includes a third column for question.no

write.csv(fisheriesTidy_922, file.path(outdir, "fisheriesTidy_922.csv"), row.names = FALSE)


event_subsets <- fisheriesTidy_922 %>%
  select(p922r__id) %>%
  unique()

event_subsets

```

## *Catch: Tuna (skipjack, yellow fin, etc.)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Tuna (skipjack, yellow fin, etc.)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Catch: Carnivorous reef fish (emperor, snapper, jacks etc.)  *

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Carnivorous reef fish (emperor, snapper, jacks etc.)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Catch: Other oceanic fish (Wahoo, mahi mahi, rainbow runner, billfish, etc.)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Other oceanic fish (Wahoo, mahi mahi, rainbow runner, billfish, etc.)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Catch: Land crab (mud crab, coconut crab, etc.)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Land crab (mud crab, coconut crab, etc.)") %>%
  filter(response != "") %>%
  filter(response != 0) # NOTE: ONLY DO THIS FOR *Catch: Land crab (mud crab, coconut crab, etc.)* - all zeroes, breaks function

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Catch: Other catch(note)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Other catch(note)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Catch: Herbivorous reef fish (parrotfish, rabbitfish, surgeonfish, etc.)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Herbivorous reef fish (parrotfish, rabbitfish, surgeonfish, etc.)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Catch: Lagoon and sand flat fish (goatfish, silver biddy, mullet, bonefish, milkfish etc)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Lagoon and sand flat fish (goatfish, silver biddy, mullet, bonefish, milkfish etc)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Catch: Lobsters*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Lobsters") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Catch: Sea worm / peanut worm (ipo worm)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Sea worm / peanut worm (ipo worm)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Catch: Other non-finfish (note) - other bivalves, ocean crabs, octopus, etc*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Other non-finfish (note) - other bivalves, ocean crabs, octopus, etc") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Catch: Cockles (arc shell, te bun)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Cockles (arc shell, te bun)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Catch: Sea snails (trochus, etc)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Sea snails (trochus, etc)") %>%
  filter(response != "") %>%
  filter(response != 0) # NOTE: Only do this for Sea snails (trochus, etc) - all zeroes breaks code

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Catch: Sea noodles / sea grapes*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Sea noodles / sea grapes") %>%
  filter(response != "") %>%
  filter(response != 0) # NOTE: Only do this for sea noodles/ sea grapes - all zeroes breaks code

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Catch: Other fish (flying fish, etc.) (note)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Other fish (flying fish, etc.) (note)") %>%
  filter(response != "") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```
## *Catch: Sharks*: No data

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

#plotDF_single <- fisheriesTidy_922 %>%
#  filter(p922r__id == "Sharks)") 

# Plot histogram
#plot_single_response(plotDF_single, bin_n = 20)

```
## *Catch: Aquarium trade (coral sponges, small colorful fish)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Aquarium trade (coral sponges, small colorful fish)") %>%
  filter(response != "") %>%
  filter(response != 0) # Only do this for aquarium trade - all zeroes - breaks function


# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Catch: Clams*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Clams") %>%
  filter(response != "") 


# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Catch: Sea cucumber*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_922 %>%
  filter(p922r__id == "Sea cucumber") %>%
  filter(response != "") %>%
  filter(response != 0) # Note: only do this for sea cucumber - all zeroes - breaks function


# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## VRS Data
### *Multi-response questions*

```{r, warning=FALSE, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Clean VRS data
#___________________________________________________________________________________________#
vrs <- read_dta(file.path(datadir, "VRS", "VRS.dta"))

vrs <- clean_data(vrs)[[1]]

# Extract variable label attributes
var_labels <- clean_data(vrs)[[2]]

# Change class to character to allow left_join without warning below
var_labels <- var_labels %>%
  mutate(col.names = as.character(col.names))

# Make tidy
vrsTidy <- tidy_data(df = vrs, pivot_col_1 = "vrs_island", pivot_col_last = "assignment__id", var_labels = var_labels, question_no = FALSE)

write.csv(vrsTidy, file.path(outdir, "vrsTidy.csv"), row.names = FALSE)


#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Bar graphs and Histograms of single/multi-select questions


# Plot bar graph for each multi-select question
plotDF_multiselect <- vrsTidy %>%
  filter(!is.na(option)) %>%
  filter(response == "1")


plot_multi_response(plotDF_multiselect)

```

## VRS continued...
### *Single response questions*


```{r, fig.height = 8, results = 'asis'}
# Plot histogram for each single response question while removing zeroes

# List short-answer, fill-in response questions here:
fill_in_questions <- vrsTidy %>%
  filter(str_detect(question, pattern = "Other")) %>% 
  pull(question) %>% 
  unique()

# Additional fill-in response questions:
fill_in_questions <- c(fill_in_questions, "Gender attending meeting", "Type of work the looking for", "New village rules")

# FIX IT - note: some short answers are still included in the single plots because they don't look too bad (e.g., "Year sewerage channel was introduced", Fee for connecting to sewage system); additional fill-in response questions are ID'ed based on eyeballing final plots

# FIX IT - confirm: assuming zero is different from "blank" (plotting function reports number of zeroes removed)
plotDF_single <- vrsTidy %>%
  filter(is.na(option)) %>%
  filter(question %in% fill_in_questions == FALSE)  %>% # remove all short answer questions 
  filter(response != "") %>% # If first response in a question set is blank, function plot_single_response does not work
  filter(question %in% c("VRS Village", "Household ID", "Start Time and Date for VRS section", "End Time and Date for VRS section",
                         "Errors count in the interview", "Status of the interview")==FALSE) # FIX IT - confirm: remove these too?

plot_single_response(plotDF_single, bin_n = 20)

# FIX IT, re-pivot so Village and/or Island are ID columns; use with color coding of scatterplots
# FIX IT, what is question = 50???
# FIX IT: how to deal with integers (bar plots) vs continuous (histogram): Number of people harvest from sea
#tmp_single <- plotDF_single %>% filter(question=="Number of people harvest from sea")
#typeof(as.numeric(tmp_single$response)) # recognized as double instead of integer

# Output short answer responses for translation
other_answers <- vrsTidy %>% 
  filter(question %in% fill_in_questions) %>%
  filter(response != "") %>% 
  unique()

write.csv(other_answers, file.path(outdir, "vrs_other_answers.csv"), row.names = FALSE)




  
```


## Event Roster Data: List of events



```{r, warning=FALSE}

#___________________________________________________________________________________________#
# Clean event roster 
#___________________________________________________________________________________________#
eventRoster <- read_dta(file.path(datadir, "VRS", "event_roster.dta"))

eventRoster <- clean_data(eventRoster)[[1]]

# Extract variable label attributes
var_labels <- clean_data(eventRoster)[[2]]

# Change class to character to allow left_join without warning below
var_labels <- var_labels %>%
  mutate(col.names = as.character(col.names))

# Make tidy
eventRosterTidy <- tidy_data(df = eventRoster, pivot_col_1 = "event_occurrence", pivot_col_last = "event_nonfinfish", var_labels = var_labels, question_no = FALSE)


# Clean responses for "Time of occurrence of event" should be years
eventRosterTidy <- eventRosterTidy %>%
  mutate(response = case_when(response == "0" ~ "2000",
                              response == "1" ~ "2001",
                              response == "2" ~ "2002",
                              response == "4" ~ "2004",
                              response == "7" ~ "2007",
                              response == "8" ~ "2008",
                              response == "10" ~ "2010",
                              TRUE ~ response))


write.csv(eventRosterTidy, file.path(outdir, "eventRosterTidy.csv"), row.names = FALSE)

event_subsets <- eventRosterTidy %>%
  select(event_roster__id) %>%
  unique()

event_subsets


```

## *Event: Coral bleaching*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- eventRosterTidy %>%
  filter(event_roster__id == "Coral bleaching event")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Event: Cyclone*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- eventRosterTidy %>%
  filter(event_roster__id == "Cyclone")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Event: Harmful algal bloom*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets


plotDF_single <- eventRosterTidy %>%
  filter(event_roster__id == "Harmful algal bloom")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Event: Tsunami*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- eventRosterTidy %>%
  filter(event_roster__id == "Tsunami")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## Fish Roster Data: List of fish assets

```{r, warning=FALSE}

#___________________________________________________________________________________________#
# Clean fish roster
#___________________________________________________________________________________________#
fishassetRoster <- read_dta(file.path(datadir, "VRS", "fish_asset_roster.dta"))

fishassetRoster <- clean_data(fishassetRoster)[[1]]

# Extract variable label attributes
var_labels <- clean_data(fishassetRoster)[[2]]

# Change class to character to allow left_join without warning below
var_labels <- var_labels %>%
  mutate(col.names = as.character(col.names))

# Make tidy
fishassetRosterTidy <- tidy_data(df = fishassetRoster, pivot_col_1 = "num_assets", pivot_col_last = "num_assets10", var_labels = var_labels, question_no = FALSE)

write.csv(fishassetRosterTidy, file.path(outdir, "fishassetRosterTidy.csv"), row.names = FALSE)

event_subsets <- fishassetRosterTidy %>%
  select(fish_asset_roster__id) %>%
  unique()

event_subsets
```
### *Asset: Fibreglass boats*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Fibreglass boats")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```
## *Asset: Outboard Motors*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Outboard Motors")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```




## *Asset: Fishing Nets (gillnet)*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Fishing Nets (gillnet)")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Asset: Spearguns*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Spearguns")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```




## *Asset: Fishing Lines*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Fishing Lines")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)
```




## *Asset: Active Fish Traps*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets
plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Active Fish Traps")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)
```





## *Asset: Underwater flashlights*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Underwater flashlights")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)
```


## *Asset: Wood canoes*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Wood canoes")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Asset: Eskies/portable coolers*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Eskies/portable coolers")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```




## *Asset: SCUBA diving equipment*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "SCUBA diving equipment")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```



## *Asset: Freezers (electric or propane)*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Freezers (electric or propane)")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```




## *Asset: Ice machines*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Ice machines")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```




## *Asset: Fishing Nets (purse)*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Fishing Nets (purse)")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Asset: Drag Nets*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Drag Nets")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```



## *Asset: Harpoons/Spears*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Harpoons/Spears")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Asset: FAD (Fish Aggregating Device)*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "FAD (Fish Aggregating Device)")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Asset: Other Fishing Equipment (note)*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Other Fishing Equipment (note)")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)




```

## Outside Roster Data: List of outside assets



```{r, warning=FALSE}
#___________________________________________________________________________________________#
# Clean outside roster
#___________________________________________________________________________________________#
outsideRoster <- read_dta(file.path(datadir, "VRS", "outside_roster.dta"))

outsideRoster <- clean_data(outsideRoster)[[1]]

# Extract variable label attributes
var_labels <- clean_data(outsideRoster)[[2]]

# Change class to character to allow left_join without warning below
var_labels <- var_labels %>%
  mutate(col.names = as.character(col.names))

# Make tidy
outsideRosterTidy <- tidy_data(df = outsideRoster, pivot_col_1 = "village_distance_out", pivot_col_last = "travel_time_out", var_labels = var_labels, question_no = FALSE)

write.csv(outsideRosterTidy, file.path(outdir, "outsideRosterTidy.csv"), row.names = FALSE)


# List short answers here:
short_answers <- c("Other transport mode outside boundary", "Travel time outside boundary")
# Short answers - units need to be standardized and some responses need to be translated

# Output short answer responses for translation
other_answers <- outsideRosterTidy %>% 
  filter(question %in% short_answers) %>%
  filter(response != "") %>% 
  unique()

write.csv(other_answers, file.path(outdir, "outsideRoster_other_answers.csv"), row.names = FALSE)

# Filter out short answer responses before moving on to plotting data subsets
outsideRosterTidy <- outsideRosterTidy %>%
  filter(question %in% short_answers == FALSE)



event_subsets <- outsideRosterTidy %>%
  select(outside_roster__id) %>%
  unique()

event_subsets


```

## *Asset: Clinic/Hospital*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Clinic/Hospital")


# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```



## *Asset: Bank*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Bank") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```




## *Asset:  Nearest Market*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Market") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```



## *Asset:  Nearest Post Office*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Post Office") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)


```




## *Asset: Nearest Credit Facility*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Credit Facility") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)


```


## *Asset: Nearest Police Station*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Police Station") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)


```






## *Asset: Nearest Court House*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Court House") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)


```


## *Asset: Airport*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Airport") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)


```




## *Asset: Nearest Trade Store/Supermarket*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Trade Store/Supermarket") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)


```




## *Asset: Nearest fish landing site*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest fish landing site") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)


```





## *Asset: Nearest Church*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Church") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)


```



## Share Roster Data: List of events



```{r, warning = FALSE}
shareRoster <- read_dta(file.path(datadir, "VRS", "share_roster.dta"))

#___________________________________________________________________________________________#
# Clean share roster
#___________________________________________________________________________________________#
shareRoster <- clean_data(shareRoster)[[1]]

# Extract variable label attributes
var_labels <- clean_data(shareRoster)[[2]]

# Change class to character to allow left_join without warning below
var_labels <- var_labels %>%
  mutate(col.names = as.character(col.names))

# Make tidy
shareRosterTidy <- tidy_data(df = shareRoster, pivot_col_1 = "catch_receiver__1", pivot_col_last = "share_other", var_labels = var_labels, question_no = FALSE)



write.csv(shareRosterTidy, "Outputs/shareRosterTidy.csv", row.names = FALSE)



# Short answers - units need to be standardized and some responses need to be translated
short_answers <- c("Other giver of the sharing of catches", "Other receiver from the sharing of catches", "Other relationship from the sharing of catches",
                   "Other sharer of the catches")

# Output short answer responses for translation
other_answers <- shareRosterTidy %>% 
  filter(question %in% short_answers) %>%
  filter(response != "") %>% 
  unique()

write.csv(other_answers, file.path(outdir, "shareRoster_other_answers.csv"), row.names = FALSE)

# Filter out short answer responses before moving on to plotting data subsets
shareRosterTidy <- shareRosterTidy %>%
  filter(question %in% short_answers == FALSE)


event_subsets <- shareRosterTidy %>%
  select(share_roster__id) %>%
  unique()

event_subsets

```




## *Asset: Finfish*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all MULTI-select questions: filter by event_subsets

plotDF_multiple_response <- shareRosterTidy %>%
  filter(share_roster__id == "Finfish")  %>%
  filter(is.na(option)==FALSE) %>% # Removes all "shared individually or through institution" question - all blank
  filter(response == "1")


# Plot histogram
plot_multi_response(plotDF_multiple_response)


```



## *Asset: Other non-finfish seafood (shellfish, sea worm, etc.)*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all MULTI-select questions: filter by event_subsets

plotDF_multiple_response <- shareRosterTidy %>%
  filter(share_roster__id == "Other non-finfish seafood (shellfish, sea worm, etc.)")  %>%
  filter(is.na(option)==FALSE) %>%
  filter(response == "1")


# Plot histogram
plot_multi_response(plotDF_multiple_response)


```




## *Asset: Non-fish foods*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all MULTI-select questions: filter by event_subsets

plotDF_multiple_response <- shareRosterTidy %>%
  filter(share_roster__id == "Non-fish foods")  %>%
  filter(is.na(option)==FALSE) %>%
  filter(response == "1")


# Plot histogram
plot_multi_response(plotDF_multiple_response)


```



## VRS Roster Data: List of events



```{r, warning=FALSE}

#___________________________________________________________________________________________#
# Clean VRS roster
#___________________________________________________________________________________________#
vrsRoster <- read_dta(file.path(datadir, "VRS", "vrs_roster.dta"))

vrsRoster <- clean_data(vrsRoster)[[1]]

# Extract variable label attributes
var_labels <- clean_data(vrsRoster)[[2]]

# Change class to character to allow left_join without warning below
var_labels <- var_labels %>%
  mutate(col.names = as.character(col.names))


# Make tidy
vrsRosterTidy <- tidy_data(df = vrsRoster, pivot_col_1 = "vrs_sex", pivot_col_last = "live_years", var_labels = var_labels, question_no = FALSE)

write.csv(vrsRosterTidy, file.path(outdir, "vrsRosterTidy.csv"), row.names = FALSE)

# Short answers - units need to be standardized and some responses need to be translated
short_answers <- c("Other position of the respondent")

# Output short answer responses for translation
other_answers <- vrsRosterTidy %>% 
  filter(question %in% short_answers) %>%
  filter(response != "") %>% 
  unique()

write.csv(other_answers, file.path(outdir, "vrsRoster_other_answers.csv"), row.names = FALSE)

# Filter out short answer responses before moving on to plotting data subsets
vrsRosterTidy <- vrsRosterTidy %>%
  filter(question %in% short_answers == FALSE)

event_subsets <- vrsRosterTidy %>%
  select(vrs_roster__id) %>%
  unique()

event_subsets


```






## *VRS Roster: 1*

```{r, fig.height = 8, results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- vrsRosterTidy %>%
  filter(vrs_roster__id == "1") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)


```


## *VRS Roster: 2*
### Note: only contains one individual with the following characteristics

```{r}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: VRS Roster 2 only contains one individual with the following characteristics

#vrsRosterTidy %>% filter(vrs_roster__id==2)


```



```{r, warning = FALSE}

#___________________________________________________________________________________________#
# Clean within roster
#___________________________________________________________________________________________#
withinRoster <- read_dta(file.path(datadir, "VRS", "within_roster.dta"))

withinRoster <- clean_data(withinRoster)[[1]]

# Extract variable label attributes
var_labels <- clean_data(withinRoster)[[2]]

# Change class to character to allow left_join without warning below
var_labels <- var_labels %>%
  mutate(col.names = as.character(col.names))

# Make tidy
withinRosterTidy <- tidy_data(df = withinRoster, pivot_col_1 = "transport_mode_within", pivot_col_last = "travel_time_within", var_labels = var_labels, question_no = FALSE)

write.csv(withinRosterTidy, file.path(outdir, "withinRosterTidy.csv"), row.names = FALSE)

# Short answers - units need to be standardized and some responses need to be translated
short_answers <- c("Other transport mode within boundary", "Travel time within boundary")

# Output short answer responses for translation
other_answers <- withinRosterTidy %>% 
  filter(question %in% short_answers) %>%
  filter(response != "") %>% 
  unique()

write.csv(other_answers, file.path(outdir, "withinRoster_other_answers.csv"), row.names = FALSE)

# Filter out short answer responses before moving on to plotting data subsets
withinRosterTidy <- withinRosterTidy %>%
  filter(question %in% short_answers == FALSE)

event_subsets <- withinRosterTidy %>%
  select(within_roster__id) %>%
  unique()

event_subsets



```





## *Asset: Nearest Church*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest Church") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Asset: Nearest Trade Store/Supermarket*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest Trade Store/Supermarket") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```



## *Asset: Airport*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Airport") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```




## *Asset: Clinic/Hospital*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Clinic/Hospital") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```




## *Asset: Nearest fish landing site*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest fish landing site") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```




## *Asset: Nearest Credit Facility*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest Credit Facility") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```



## *Asset: Nearest Market*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest Market") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Asset: Nearest Post Office*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest Post Office") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```



## *Asset: Nearest Court House*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest Court House") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Asset: Bank*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Bank") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


### Market survey
## Food availability

```{r, warning = FALSE, message = FALSE, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Clean market data
#___________________________________________________________________________________________#
market.files <- list.files("Data/HIES_raw_19May20/Market Survey")

# ID unique food items
food.files <- unique(gsub("_.*", '', market.files))
food.files <- food.files[food.files != "MarketSurvey.dta"]

food.items <- food.files
food.items[food.items == "veges"] <- "vege" # make singular (have to keep plural to read in file)

# Combine food and unit rosters
food.roster <- read_dta(file.path("Data", "HIES_raw_19May20", "Market Survey", 
                                    paste(food.files[1], "roster.dta", sep ="_")))
unit.roster <- read_dta(file.path("Data", "HIES_raw_19May20", "Market Survey", 
                                    paste(food.files[1], "unit", "roster.dta", sep ="_")))

# FIX IT - JG, not understanding what this was for:
# Standardize column names
colnames(food.roster) <- gsub(paste(food.items[1], "s", sep = ""), paste(food.items[1]), colnames(food.roster))
colnames(unit.roster) <- gsub(paste(food.items[1], "s", sep = ""), paste(food.items[1]), colnames(unit.roster))

# Merge by roster__id column (but not unit_roster__id column)
marketSurvey <- full_join(food.roster, unit.roster, by = c("interview__key", "interview__id", paste(food.items[1], "roster__id", sep ="_")))

# Clean and extract variable label attributes
marketSurvey <- clean_data(marketSurvey)[[1]]


# Remove y/n units columns and rename others
select.cols <- c("interview__key", "interview__id", 
                 paste(food.items[1], "roster__id", sep = "_"),
                 paste("other", food.items[1], "units", sep = "_"),
                 paste(food.items[1], "available", sep = "_"),
                 paste(food.items[1], "avail_oth", sep = "_"),
                 paste(food.items[1], "unit_roster__id", sep = "_"),
                 paste(food.items[1], "price", sep = "_"),
                 paste(food.items[1], "weight", sep = "_"),
                 paste(food.items[1], "unit_oth", sep = "_")
                 )
marketSurvey <- marketSurvey %>% 
  select_at(vars(select.cols))

# Standardize column names
colnames(marketSurvey) <- c("interview__key", "interview__id", "roster__id","other_units","availability","availability_other",
                            "unit_roster__id","price","weight", "unit_other")


for(i in 2:length(food.items)){
  food.roster <- read_dta(file.path("Data", "HIES_raw_19May20", "Market Survey", 
                                    paste(food.files[i], "roster.dta", sep ="_")))
  unit.roster <- read_dta(file.path("Data", "HIES_raw_19May20", "Market Survey", 
                                    paste(food.files[i], "unit", "roster.dta", sep ="_")))
  
  # Standardize column names
  colnames(food.roster) <- gsub(paste(food.items[i], "s", sep = ""), paste(food.items[i]), colnames(food.roster))
  colnames(unit.roster) <- gsub(paste(food.items[i], "s", sep = ""), paste(food.items[i]), colnames(unit.roster))

  # Merge by roster__id column (but not unit_roster__id column)
  food.unit.roster <- full_join(food.roster, unit.roster, by = c("interview__key", "interview__id", paste(food.items[i], "roster__id", sep ="_")))

  # Clean and extract variable label attributes
  food.unit.roster <- clean_data(food.unit.roster)[[1]]

  
  # Remove y/n units columns and rename others
  select.cols <- c("interview__key", "interview__id", 
                 paste(food.items[i], "roster__id", sep = "_"),
                 paste("other", food.items[i], "units", sep = "_"),
                 paste(food.items[i], "available", sep = "_"),
                 paste(food.items[i], "avail_oth", sep = "_"),
                 paste(food.items[i], "unit_roster__id", sep = "_"),
                 paste(food.items[i], "price", sep = "_"),
                 paste(food.items[i], "weight", sep = "_"),
                 paste(food.items[i], "unit_oth", sep = "_")
                 )
  food.unit.roster <- food.unit.roster %>% 
    select_at(vars(select.cols))

# Standardize column names
colnames(food.unit.roster) <- c("interview__key", "interview__id", "roster__id","other_units","availability","availability_other",
                            "unit_roster__id","price","weight", "unit_other")
  
  # Join with marketSurvey to create join all foods
  marketSurvey <- bind_rows(marketSurvey, food.unit.roster)
}

# Merge with survey location info
survey.info <- read_dta(file.path("Data", "HIES_raw_19May20", "Market Survey", "MarketSurvey.dta"))
survey.info <- clean_data(survey.info)[[1]]

survey.info <- survey.info %>%
  select("interview__key", "interview__id", "ms_island", "ms_village", "ea_market")

marketSurvey <- full_join(survey.info, marketSurvey, by = c("interview__key", "interview__id"))

# Plot food item availability
plot.food.availability(marketSurvey)

```




### Market survey continued... 
## Food prices

```{r, warning = FALSE, message = FALSE, fig.height = 8, results = 'asis'}

# Clean price data

# Question for Mike: why are their duplicates in price information within marketSurvey?
market_survey_price_duplicates <- marketSurvey %>% group_by(interview__id, roster__id, price, weight) %>% summarise(n=n()) %>% filter(n>1) %>% left_join(marketSurvey, by = c("interview__id", "roster__id", "price", "weight")) %>% ungroup() %>% select(-n) %>% arrange(interview__id)
write.csv(market_survey_price_duplicates, file = file.path(outdir, "market_survey_price_duplicates.csv"), row.names = FALSE) # n = 68


# FOODS WITH NO WEIGHT UNITS:
market_survey_no_weight_unit <- marketSurvey %>%
  mutate(unit_roster__id = as.character(unit_roster__id)) %>%
  filter(unit_roster__id %in% c("Bundle / Bunch / Pack", "Each / Piece", "Can / Bottle", "Box / Carton", "Bag", "Other units", "Bucket", "Plate / Bowl", "Basket") & is.na(unit_other))
write.csv(market_survey_no_weight_unit, file = file.path(outdir, "market_survey_no_weight_unit.csv"), row.names = FALSE) # n = 1

# FOODS WITH NO WEIGHT MEASUREMENT (usually things that are measured with unit_roster__id == Each/Piece usually also has an entry for weight and unit_other, but these do not)
market_survey_no_weight <- marketSurvey %>% 
  filter(weight ==0)
write.csv(market_survey_no_weight, file = file.path(outdir, "market_survey_no_weight.csv"), row.names = FALSE) # n = 17


# STANDARDIZE PRICES
market_survey_price <- marketSurvey %>% 
  group_by(interview__id, roster__id, price, weight) %>% 
  mutate(n=n()) %>% 
  arrange(desc(n)) %>% 
  filter(row_number()==1) %>% 
  ungroup() %>% 
  select(-n) %>%
  arrange(interview__id) %>% 
  # Where it exists, use unit_other to replace unit_roster__id, but first mutate to character
  mutate(unit_roster__id = as.character(unit_roster__id),
         unit_other = as.character(unit_other)) %>%
  mutate(unit_roster__id = if_else(is.na(unit_other)==FALSE, true = unit_other, false = unit_roster__id)) %>%
  # Filter out foods with no weight units (n=1):
  filter(unit_roster__id != "Each / Piece") %>% 
  # Filter out foods with no weight measurements (n=17)
  filter(weight != 0) %>% 
  # Standardize FORMAT of units: (g) Grams vs grams (g) 
  mutate(unit_roster__id = case_when(unit_roster__id == "grams (g)" ~ "(g) Grams",
                                     unit_roster__id == "Pounds (lb)" ~ "(lbs) Pounds",
                                     unit_roster__id == "Kilograms (kg)" ~ "(kg) Kilograms",
                                     unit_roster__id == "(kg) Kilo-grams" ~ "(kg) Kilograms",
                                     TRUE ~ unit_roster__id)) %>%
  # Standardize units (first, standardize WITHIN metric and within US units)
  mutate(weight = if_else(unit_roster__id == "(kg) Kilograms", true = weight * 1000, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(kg) Kilograms", true = "(g) Grams", false = unit_roster__id)) %>%
  mutate(weight = if_else(unit_roster__id == "(ml) Milliliters", true = weight / 1000, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(ml) Milliliters", true = "(ltr) Litres", false = unit_roster__id)) %>%
  mutate(weight = if_else(unit_roster__id == "(lbs) Pounds", true = weight * 16, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(lbs) Pounds", true = "(oz) Ounces", false = unit_roster__id)) %>%
  mutate(weight = if_else(unit_roster__id == "(c) Cups", true = weight / 16, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(c) Cups", true = "(gal) Gallons", false = unit_roster__id)) %>%
  mutate(weight = if_else(unit_roster__id == "(pt) Pints", true = weight / 8, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(pt) Pints", true = "(gal) Gallons", false = unit_roster__id)) %>%
  mutate(weight = if_else(unit_roster__id == "(qt) Quarts", true = weight / 4, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(qt) Quarts", true = "(gal) Gallons", false = unit_roster__id)) %>%
  # Standardize all to metric (convert ounces to grams, gallons to liters)
  mutate(weight = if_else(unit_roster__id == "(oz) Ounces", true = weight * 28.35, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(oz) Ounces", true = "(g) Grams", false = unit_roster__id)) %>%
  mutate(weight = if_else(unit_roster__id == "(gal) Gallons", true = weight * 3.78, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(gal) Gallons", true = "(ltr) Litres", false = unit_roster__id)) %>%
  # Now calculate PRICE per UNIT WEIGHT
  mutate(standardized_price = price / weight)

# NOW PLOT:

plot.food.prices(market_survey_price)
  
# FOODS with mixed units:  note, can get this list by allowing print(food) to run in plot.food.prices function
mixed_units <- c("Cordial, syrup, not further specified",
                 "Cooking oil &amp; fats",
                 "Canned meat, corned beef",
                 "Chocolate in bars or in slabs",
                 "Toffees, pastilles and other confectionery products",
                 "Other non alcoholic beverages",
                 "Noodles, pasta",
                 "Other diary and oil product",
                 "Brown coconut",
                 "Chewing gum",
                 "Ice block, icies, ice frubu etc",
                 "Chinese sweets (mango skin, pawpaw skin etc",
                 "Ice cream",
                 "Bottled water/spring water/mineral water",
                 "Cola flavour soft drink eg. Coca cola/Pepsi",
                 "Soft drinks (Fizzy), eg. Sprite, 7 Up, Tonic, Fanta,",
                 "Fruit juice (apple, pineapple, tropical etc...)",
                  "Lollies",
                 "Ice cream cones",
                 "Other fruit (specify)"
                 )


market_survey_diff_units <- market_survey_price %>%
  filter(roster__id %in% mixed_units) %>%
  arrange(roster__id)

write.csv(market_survey_diff_units, file = file.path(outdir, "market_survey_diff_units.csv"), row.names = FALSE)



```












