---
title: "Exploratory figures for CNHS"
author: "Kelvin Gorospe and Jessica Gephart"
date: "10/15/2020"
output: pdf_document
---

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(haven)
library(tidyverse)
library(magrittr)
library(ggplot2)

#___________________________________________________________________________________________#
# Read in tidy data files
# ___________________________________________________________________________________________#
# Note: datadir and outdir are the same now that data cleaning is done separately in clean_vrs and clean_market.R 
datadir <- "/Volumes/jgephart/Kiribati/Outputs"
outdir <- "/Volumes/jgephart/Kiribati/Outputs"

source("R_scripts/plotting_functions.R")

# VRS Data:
vrsTidy <- read.csv(file.path(datadir, "vrsTidy.csv"))
eventRosterTidy <- read.csv(file.path(datadir, "eventRosterTidy.csv"))
fishassetRosterTidy <- read.csv(file.path(datadir, "fishassetRosterTidy.csv"))
outsideRosterTidy <- read.csv(file.path(datadir, "outsideRosterTidy.csv"))
shareRosterTidy <- read.csv(file.path(datadir, "shareRosterTidy.csv"))
vrsRosterTidy <- read.csv(file.path(datadir, "vrsRosterTidy.csv"))
withinRosterTidy <- read.csv(file.path(datadir, "withinRosterTidy.csv"))

# Market Data:
marketSurveyTidy <- read.csv(file.path(datadir, "marketSurveyTidy.csv"))

```

## VRS Data
### *Multi-response questions*

```{r, warning=FALSE, fig.height = 8, fig.width = 8,  results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Bar graphs and Histograms of single/multi-select questions

# Plot bar graph for each multi-select question
plotDF_multiselect <- vrsTidy %>%
  filter(!is.na(option)) %>%
  filter(response == "1")

plot_multi_response(plotDF_multiselect, incl_island = TRUE)

```

## VRS continued...
### *Single response questions*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}
# Plot histogram for each single response question while removing zeroes

# List short-answer, fill-in response questions here:
fill_in_questions <- vrsTidy %>%
  filter(str_detect(question, pattern = "Other") & question != "Other meeting restrictions") %>% 
  pull(question) %>% 
  unique()

# Additional fill-in response questions:
fill_in_questions <- c(fill_in_questions, "Gender attending meeting", "New village rules")

# FIX IT - confirm: assuming zero is different from "blank" (plotting function reports number of zeroes removed)
plotDF_single <- vrsTidy %>%
  filter(is.na(option)) %>%
  filter(question %in% fill_in_questions == FALSE)  %>% # remove all short answer questions 
  filter(response != "") %>% # If first response in a question set is blank, function plot_single_response does not work
  filter(question %in% c("VRS Village", "Household ID", "Start Time and Date for VRS section", "End Time and Date for VRS section",
                         "Errors count in the interview", "Status of the interview")==FALSE) # FIX IT - confirm: remove these too?

plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## Event Roster Data: List of events

```{r, warning=FALSE}

event_subsets <- eventRosterTidy %>%
  select(event_roster__id) %>%
  unique()

event_subsets

```

## *Event: Coral bleaching*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- eventRosterTidy %>%
  filter(event_roster__id == "Coral bleaching event")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20,incl_island = TRUE)

```

## *Event: Cyclone*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- eventRosterTidy %>%
  filter(event_roster__id == "Cyclone")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Event: Harmful algal bloom*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- eventRosterTidy %>%
  filter(event_roster__id == "Harmful algal bloom")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Event: Tsunami*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- eventRosterTidy %>%
  filter(event_roster__id == "Tsunami")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## Fish Roster Data: List of fish assets

```{r, warning=FALSE}
event_subsets <- fishassetRosterTidy %>%
  select(fish_asset_roster__id) %>%
  unique()

event_subsets
```

### *Asset: Fibreglass boats*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Fibreglass boats")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```
## *Asset: Outboard Motors*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Outboard Motors")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Fishing Nets (gillnet)*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Fishing Nets (gillnet)")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Spearguns*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Spearguns")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Fishing Lines*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Fishing Lines")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)
```

## *Asset: Active Fish Traps*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets
plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Active Fish Traps")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)
```

## *Asset: Underwater flashlights*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Underwater flashlights")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)
```

## *Asset: Wood canoes*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Wood canoes")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Eskies/portable coolers*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Eskies/portable coolers")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: SCUBA diving equipment*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "SCUBA diving equipment")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Freezers (electric or propane)*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Freezers (electric or propane)")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Ice machines*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Ice machines")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Fishing Nets (purse)*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Fishing Nets (purse)")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Drag Nets*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Drag Nets")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Harpoons/Spears*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Harpoons/Spears")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: FAD (Fish Aggregating Device)*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "FAD (Fish Aggregating Device)")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Other Fishing Equipment (note)*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fishassetRosterTidy %>%
  filter(fish_asset_roster__id == "Other Fishing Equipment (note)")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## Outside Roster Data: List of outside assets

```{r, warning=FALSE}

#Filter out short answer responses before moving on to plotting data subsets
short_answers <- c("Other transport mode outside boundary", "Travel time outside boundary")
outsideRosterTidy <- outsideRosterTidy %>%
  filter(question %in% short_answers == FALSE)

event_subsets <- outsideRosterTidy %>%
  select(outside_roster__id) %>%
  unique()

event_subsets

```

## *Asset: Clinic/Hospital*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Clinic/Hospital")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Bank*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Bank") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset:  Nearest Market*

```{r}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Market") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset:  Nearest Post Office*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Post Office") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Nearest Credit Facility*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Credit Facility") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Nearest Police Station*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Police Station") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Nearest Court House*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Court House") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Airport*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Airport") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Nearest Trade Store/Supermarket*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Trade Store/Supermarket") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Nearest fish landing site*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest fish landing site") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Nearest Church*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- outsideRosterTidy %>%
  filter(outside_roster__id == "Nearest Church") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## Share Roster Data: List of events

```{r, warning = FALSE}

# Filter out short answer responses before moving on to plotting data subsets
shareRosterTidy <- shareRosterTidy %>%
  filter(question %in% short_answers == FALSE)

event_subsets <- shareRosterTidy %>%
  select(share_roster__id) %>%
  unique()

event_subsets
```

## *Asset: Finfish*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all MULTI-select questions: filter by event_subsets

plotDF_multiple_response <- shareRosterTidy %>%
  filter(share_roster__id == "Finfish")  %>%
  filter(is.na(option)==FALSE) %>% # Removes all "shared individually or through institution" question - all blank
  filter(response == "1")

# Plot histogram
plot_multi_response(plotDF_multiple_response, incl_island = TRUE)
```

## *Asset: Other non-finfish seafood (shellfish, sea worm, etc.)*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all MULTI-select questions: filter by event_subsets

plotDF_multiple_response <- shareRosterTidy %>%
  filter(share_roster__id == "Other non-finfish seafood (shellfish, sea worm, etc.)")  %>%
  filter(is.na(option)==FALSE) %>% # Removes all "shared individually or through institution" question - all blank
  filter(response == "1")

# Plot histogram
plot_multi_response(plotDF_multiple_response, incl_island = TRUE)

```

## *Asset: Non-fish foods*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all MULTI-select questions: filter by event_subsets

plotDF_multiple_response <- shareRosterTidy %>%
  filter(share_roster__id == "Non-fish foods")  %>%
  filter(is.na(option)==FALSE) %>% # Removes all "shared individually or through institution" question - all blank
  filter(response == "1")

# Plot histogram
plot_multi_response(plotDF_multiple_response, incl_island = TRUE)

```

## VRS Roster Data: List of events

```{r, warning=FALSE}

# Filter out short answer responses before moving on to plotting data subsets
vrsRosterTidy <- vrsRosterTidy %>%
  filter(question %in% short_answers == FALSE)

event_subsets <- vrsRosterTidy %>%
  select(vrs_roster__id) %>%
  unique()

event_subsets
```

## *VRS Roster: 1*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}

#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- vrsRosterTidy %>%
  filter(vrs_roster__id == "1") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *VRS Roster: 2*
### Note: only contains one individual

```{r}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: VRS Roster 2 only contains one individual with the following characteristics

#vrsRosterTidy %>% filter(vrs_roster__id==2)

```

## Within Roster Data: List of events

```{r, warning = FALSE}

# Filter out short answer responses before moving on to plotting data subsets
short_answers <- c("Other transport mode within boundary", "Travel time within boundary")

withinRosterTidy <- withinRosterTidy %>%
  filter(question %in% short_answers == FALSE)

event_subsets <- withinRosterTidy %>%
  select(within_roster__id) %>%
  unique()

event_subsets

```

## *Asset: Nearest Church*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest Church") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Nearest Trade Store/Supermarket*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest Trade Store/Supermarket") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Airport*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Airport") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Clinic/Hospital*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Clinic/Hospital") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Nearest fish landing site*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest fish landing site") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Nearest Credit Facility*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest Credit Facility") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Nearest Market*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest Market") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Nearest Post Office*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest Post Office") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Nearest Court House*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Nearest Court House") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

## *Asset: Bank*

```{r, fig.height = 8, fig.width = 8,  results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- withinRosterTidy %>%
  filter(within_roster__id == "Bank") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20, incl_island = TRUE)

```

### *Market survey*
## Food availability

```{r, warning=FALSE, message=FALSE, fig.height = 8, fig.width = 8,  results = 'asis'}

# Plot food item availability
plot.food.availability(marketSurveyTidy, incl_island = TRUE)

```

### Market survey continued... 
## Food prices

```{r, warning = FALSE, message = FALSE, fig.height = 8, results = 'asis'}

# STANDARDIZE PRICES before plotting
market_survey_price <- marketSurveyTidy %>% 
  group_by(interview__id, roster__id, price, weight) %>% 
  mutate(n=n()) %>% 
  #arrange(desc(n)) %>% 
  filter(row_number()==1) %>% # just keep one entry per group
  ungroup() %>% 
  select(-n) %>%
  arrange(interview__id) %>% 
  # Where it exists, use unit_other to replace unit_roster__id, but first mutate to character
  mutate(unit_roster__id = as.character(unit_roster__id),
         unit_other = as.character(unit_other)) %>%
  mutate(unit_roster__id = if_else(is.na(unit_other)==FALSE, true = unit_other, false = unit_roster__id)) %>%
  # Filter out foods with no weight units (n=1):
  filter(unit_roster__id != "Each / Piece") %>% 
  # Filter out foods with no weight measurements (n=17)
  filter(weight != 0) %>% 
  # Standardize FORMAT of units: (g) Grams vs grams (g) 
  mutate(unit_roster__id = case_when(unit_roster__id == "grams (g)" ~ "(g) Grams",
                                     unit_roster__id == "Pounds (lb)" ~ "(lbs) Pounds",
                                     unit_roster__id == "Kilograms (kg)" ~ "(kg) Kilograms",
                                     unit_roster__id == "(kg) Kilo-grams" ~ "(kg) Kilograms",
                                     TRUE ~ unit_roster__id)) %>%
  # Standardize units (first, standardize WITHIN metric and within US units)
  mutate(weight = if_else(unit_roster__id == "(kg) Kilograms", true = weight * 1000, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(kg) Kilograms", true = "(g) Grams", false = unit_roster__id)) %>%
  mutate(weight = if_else(unit_roster__id == "(ml) Milliliters", true = weight / 1000, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(ml) Milliliters", true = "(ltr) Litres", false = unit_roster__id)) %>%
  mutate(weight = if_else(unit_roster__id == "(lbs) Pounds", true = weight * 16, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(lbs) Pounds", true = "(oz) Ounces", false = unit_roster__id)) %>%
  mutate(weight = if_else(unit_roster__id == "(c) Cups", true = weight / 16, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(c) Cups", true = "(gal) Gallons", false = unit_roster__id)) %>%
  mutate(weight = if_else(unit_roster__id == "(pt) Pints", true = weight / 8, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(pt) Pints", true = "(gal) Gallons", false = unit_roster__id)) %>%
  mutate(weight = if_else(unit_roster__id == "(qt) Quarts", true = weight / 4, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(qt) Quarts", true = "(gal) Gallons", false = unit_roster__id)) %>%
  # Standardize all to metric (convert ounces to grams, gallons to liters)
  mutate(weight = if_else(unit_roster__id == "(oz) Ounces", true = weight * 28.35, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(oz) Ounces", true = "(g) Grams", false = unit_roster__id)) %>%
  mutate(weight = if_else(unit_roster__id == "(gal) Gallons", true = weight * 3.78, false = weight),
         unit_roster__id = if_else(unit_roster__id == "(gal) Gallons", true = "(ltr) Litres", false = unit_roster__id)) %>%
  # Now calculate PRICE per UNIT WEIGHT
  mutate(standardized_price = price / weight)

# Plot prices:
plot.food.prices(market_survey_price, incl_island = TRUE)
```
