---
title: "SE_traps_figs"
author: "Jessica Gephart"
date: "10/15/2019"
output: pdf_document
---

```{r, echo=FALSE}
# Load packages and raw data

library(tidyverse)
library(ggplot2)
library(countrycode)

trade_raw <- read.csv("Data/FoodBalanceSheets_E_All_Data.csv")
health_raw <- read.csv("Data/SIDS_NCDs.csv")
reefs_raw <- read.csv() # Need data from Jacob

```


```{r, echo=FALSE}
# Clean raw data and create single DF

# Clean trade data
trade_clean <- trade_raw %>% 
  filter(Element %in% c("Import Quantity", "Domestic supply quantity")) %>%
  select(-c("Element.Code")) %>% 
  select(-ends_with("F")) %>%
  gather("year", "value", Y1961:Y2013) %>%
  spread(Element, value) 
trade_clean$`Domestic supply quantity`<- as.numeric(trade_clean$`Domestic supply quantity`)
trade_clean$`Import Quantity` <- as.numeric(trade_clean$`Import Quantity`)

trade_clean <- trade_clean %>%
  group_by(Area.Code, Area, Unit, year) %>%
  summarise(Total_supply = sum(`Domestic supply quantity`, na.rm = TRUE), Total_import = sum(`Import Quantity`, na.rm = TRUE)) %>% 
  mutate(Percent_import = 100*(Total_import/Total_supply))

trade_clean$year <- str_remove(trade_clean$year, pattern = "Y")
trade_clean$year <- as.numeric(trade_clean$year)
trade_clean$country.code <- countrycode(trade_clean$Area, origin = "country.name", destination = "iso3c")
trade_clean <- trade_clean %>%
  filter(is.na(country.code) == FALSE)

# CLean health data
health_raw$country.code <- countrycode(health_raw$location_name, origin = "country.name", destination = "iso3c")
health_clean <- health_raw %>%
  filter(is.na(country.code) == FALSE) %>%
  filter(metric_name == "Percent") %>%
  select(country.code, location_name, year, measure_name, cause_name, val) %>%
  spread(measure_name, val)


# Merge data
df <- inner_join(health_clean, trade_clean, by = c("year", "country.code"))

```

```{r, echo=FALSE}
# Exploratory figures
df_plot <- df %>%
  filter(year == 2013) %>%
  filter(cause_name == "Cardiovascular diseases")

ggplot(df_plot, aes(x = Percent_import, y = Prevalence)) +
  geom_point()


```

reefs_raw <- read.csv(file="SIDS OHI 2012-2018.csv", header=TRUE) # JE stuff down here, I dont understand "```{r, echo=FALSE}" these
 
# Clean reef data
reefs_raw$country.code <- countrycode(reefs_raw$location_name, origin = "country.name", destination = "iso3c") # added new column with country code ID
reefs_raw$year <- as.numeric(as.character(reefs_raw$year))
reefs_clean <- reefs_raw %>%
  select(country.code, location_name, year, OHI_val)

reefs_clean <- reefs_clean[-which(reefs_clean$year == '2018'),] #2014b to 2018 cant be compared with 2012 to 2014 in the data (different sources)
reefs_clean <- reefs_clean[-which(reefs_clean$year == '2017'),]
reefs_clean <- reefs_clean[-which(reefs_clean$year == '2016'),]
reefs_clean <- reefs_clean[-which(reefs_clean$year == '2015'),]

reefs_clean <- reefs_clean %>%
  filter(is.na(country.code) == FALSE) %>%
  filter(is.na(year) == FALSE)

# Merge data
df <- inner_join(health_clean, trade_clean, by = c("year", "country.code"))
df <- inner_join(df, reefs_clean, by = c("year", "country.code"))

# Exploratory figures
df_plot <- df %>%
  filter(year == 2012) %>%
  filter(cause_name == "Cardiovascular diseases")
ggplot(df_plot, aes(x = Percent_import, y = Prevalence, fill = OHI_val, color = OHI_val)) +
  geom_point() + geom_smooth(method = "lm", color = "darkred", se = TRUE) + geom_text(aes(label=country.code), size=3, hjust = -0.1) +
  theme_classic()
