---
title: 'HIES Data: Exploratory figures for CNHS'
author: "Kelvin Gorospe and Jessica Gephart"
date: "10/15/2020"
output: html_document
---

Notes: This was originally part of the prelim_VRS_and_market_survey_review.Rmd file; now separating HIES data into separate Rmd file here

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(tidyverse)
library(magrittr)
library(ggplot2)

#___________________________________________________________________________________________#
# Read in Tidy data files
#___________________________________________________________________________________________#
# Note: datadir and outdir are the same now that data cleaning is done separately in clean_vrs and clean_market.R 
datadir <- "/Volumes/jgephart/Kiribati/Outputs"
outdir <- "/Volumes/jgephart/Kiribati/Outputs"
source("R_scripts/plotting_functions.R")

# FIX IT - read in all HIES Tidy data up top here

```

## Fisheries continued...
### *Single response questions*


```{r, fig.height = 8, results = 'asis'}

# List short-answer, fill-in response questions here:
fill_in_questions <- c("p903n", "p921n", "p922n1", "p922n2")

# Plot histogram for each single response question while removing zeroes
plotDF_single <- fisheriesTidy %>%
  filter(is.na(option)) %>%
  filter(question.no %in% fill_in_questions == FALSE) # remove "other" responses

plot_single_response(plotDF_single, bin_n = 20)
  

# Output short answer responses for translation
other_answers <- fisheriesTidy %>% 
  filter(question.no %in% fill_in_questions) %>%
  filter(response != "") %>% 
  unique()

write.csv(other_answers, file.path(outdir, "fisheries_other_answers.csv"), row.names = FALSE)




```



## Other Fisheries (p903r) data


```{r, warning = FALSE}

#___________________________________________________________________________________________#
# Clean fisheries data
#___________________________________________________________________________________________#
fisheries_903 <- read_dta(file.path(datadir, "Fisheries", "p903r.dta"))

fisheries_903 <- clean_data(fisheries_903)[[1]]

# Extract variable label attributes
var_labels <- clean_data(fisheries_903)[[2]]

# Change class to character to allow left_join without warning below
var_labels <- var_labels %>%
  mutate(col.names = as.character(col.names))

# Make tidy
fisheriesTidy_903 <- pivot_data_long(df = fisheries_903, pivot_col_1 = "p904", pivot_col_last = "p910", var_labels = var_labels, question_no = TRUE) # question_no = TRUE applies to fisheries data where col.labels includes a third column for question.no

write.csv(fisheriesTidy_903, file.path(outdir, "fisheriesTidy_903.csv"), row.names = FALSE)


# Output short answer responses for translation
short_answers <- c("other method of transportation")
# Short answers - units need to be standardized and some responses need to be translated

other_answers <- fisheriesTidy_903 %>% 
  filter(question %in% short_answers) %>%
  filter(response != "") %>% 
  unique() %>%
  arrange(question)

write.csv(other_answers, file.path(outdir, "fisheries_903R_other_answers.csv"), row.names = FALSE)


# Filter out short answer responses before moving on to plotting data subsets
fisheriesTidy_903 <- fisheriesTidy_903 %>%
  filter(question %in% short_answers == FALSE)




event_subsets <- fisheriesTidy_903 %>%
  select(p903r__id) %>%
  unique()

event_subsets


```

## *Fishing Method: Trolling, jigging or deep water line fishing*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Trolling, jigging or deep water line fishing - Te kasiki") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Fishing Method: Handline (drop stone, pole fishing, rod &amp; reel) - Te karekare*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Handline (drop stone, pole fishing, rod &amp; reel) - Te karekare") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```


## *Fishing Method: Gleaning / Collecting*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Gleaning / Collecting") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Fishing Method: Other (note)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Other (note)") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Fishing Method: Spearfishing night (Te katebe te tairiki)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Spearfishing night (Te katebe te tairiki)") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Fishing Method: Spearfishing day ((Te katebe te ngaina)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Spearfishing day ((Te katebe te ngaina)") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## *Fishing Method: Net (beach seine, gill, cast) - Te karaun*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Net (beach seine, gill, cast) - Te karaun") 

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```
## *Fishing Method: Freediving / diving without SCUBA (Te tebo)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Freediving / diving without SCUBA (Te tebo)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```
## *Fishing Method: Traps (Te uu)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Traps (Te uu)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```
## *Fishing Method: Diving with SCUBA (Te tebo me te bwai n ikeike)*

```{r, fig.height = 8, results = 'asis'}
#___________________________________________________________________________________________#
# Visualize data
#___________________________________________________________________________________________#
# Note: Roster is all single-select questions: no filtering needed; subset by event_subsets

plotDF_single <- fisheriesTidy_903 %>%
  filter(p903r__id == "Diving with SCUBA (Te tebo me te bwai n ikeike)") %>%
  filter(response != "")

# Plot histogram
plot_single_response(plotDF_single, bin_n = 20)

```

## p903 continued: CPUE

```{r, fig.height = 8, results = 'asis'}

cpue_pivot <- fisheriesTidy_903 %>%
  filter(question %in% c("hours spent on the trip to access current method",
                         "number of fishing trips",
                         "hours spent on current method",
                         "weight of catch using current method")) %>%
  select(-question.no) %>%
  pivot_wider(names_from = question, values_from = response)

cpue_summary <- cpue_pivot %>%
  mutate_at(vars(`hours spent on the trip to access current method`,
                 `weight of catch using current method`, 
                 `number of fishing trips`,
                 `hours spent on current method`), as.numeric) %>%
  group_by(interview__id, hm_basic__id, p903r__id) %>% # group_by interviewee, household member (sometimes multiple interviews per houselhold) and fishing gear
  summarise(cpue = `weight of catch using current method` / (`hours spent on the trip to access current method` * `hours spent on current method` * `number of fishing trips`)) %>%
  ungroup()

### NOTE: There are zeroes in all time columns (i.e., `hours spent on the trip to access current method`, `hours spent on current method`, `number of fishing trips`)
# meaning no matter which column is used, CPUE is undefined (catch divided by zero) for certain respondents

# FIX IT - turn this into a function?
for (i in 1:length(unique(cpue_summary$p903r__id))) {
  
  fishing_method <- unique(cpue_summary$p903r__id)[i]
  
  cpue_plot <- cpue_summary %>% 
    filter(p903r__id == fishing_method) %>%
    filter(cpue != "Inf") %>% # filters out when denominator is zero
    filter(is.na(cpue)==FALSE) # filters out when numerator and denominator is zero
  
  p <- ggplot(cpue_plot, aes(x = cpue)) +
    geom_histogram(bins = 20) +
    labs(title = fishing_method, y = "", x = "CPUE")

  # Print out each plot within R
  print(p)
  # Go to new page before printing next figure
  cat("\n\n\\newpage\n")

}

```

## Other Fisheries (p922r) data

```{r, warning = FALSE}

#___________________________________________________________________________________________#
# Clean fisheries data
#___________________________________________________________________________________________#
fisheries_922 <- read_dta(file.path(datadir, "Fisheries", "p922r.dta"))

fisheries_922 <- clean_data(fisheries_922)[[1]]

# Extract variable label attributes
var_labels <- clean_data(fisheries_922)[[2]]

# Change class to character to allow left_join without warning below
var_labels <- var_labels %>%
  mutate(col.names = as.character(col.names))

# Make tidy
fisheriesTidy_922 <- pivot_data_long(df = fisheries_922, pivot_col_1 = "p923", pivot_col_last = "p925", var_labels = var_labels, question_no = TRUE) # question_no = TRUE applies to fisheries data where col.labels includes a third column for question.no

write.csv(fisheriesTidy_922, file.path(outdir, "fisheriesTidy_922.csv"), row.names = FALSE)

event_subsets <- fisheriesTidy_922 %>%
  select(p922r__id) %>%
  unique()

event_subsets

```